### 2011-06-24 docs/architecture/architecture.tex
list of tables

\item {\tt bcx\_lo }, {\tt bcy\_lo }, {\tt bcz\_lo }, 
      {\tt bcx\_hi }, {\tt bcy\_hi }, {\tt bcz\_hi } are the boundary
   condition types at the lower (`{\tt lo}') and upper (`{\tt hi}')
   domain boundaries in the $x$, $y$, and $z$ coordinate directions.
   The different types are set via integer flags noted below:

   \begin{center}
   \begin{tabular}{ll}
   \hline
   BC type    & integer flag \\
   \hline
   periodic             & $-1$ \\
   inlet (user-defined) & $11$ \\
   outlet               & $12$ \\
   symmetry             & $13$ \\
   slip wall            & $14$ \\
   no-slip wall         & $15$ \\
   \hline
   \end{tabular}
   \end{center}

@@

The first argument to the {\tt eos} call is an integer key that
specifies which thermodynamic variables (in addition to the mass
fractions) are used as input.  Options include:

   \begin{center}
   \begin{tabular}{lc}
   \hline
   key            & input quantities \\
   \hline
   {\tt eos\_input\_rt}       & $\rho$, $T$ \\
   {\tt eos\_input\_rh}       & $\rho$, $h$ \\
   {\tt eos\_input\_tp}       & $T$, $p$ \\
   {\tt eos\_input\_rp}       & $\rho$, $p$ \\
   {\tt eos\_input\_re}       & $\rho$, $e$ \\
   {\tt eos\_input\_ps}       & $p$, $s$ \\
   \hline
   \end{tabular}
   \end{center}

@@

The {\tt variables} module provides integer keys to index the state
multifabs and other arrays dealing with the scalar quantities.  The
most commonly used keys are are:

\begin{center}
\begin{tabular}{ll}
\hline
{\tt rho\_comp}  & density \\
{\tt rhoh\_comp} & density $\times$ specific enthalpy, $(\rho h)$ \\
{\tt spec\_comp} & first species partial density, $(\rho X_1)$ \\
{\tt temp\_comp} & temperature \\
\hline
\end{tabular}
\end{center}

>>>>

\item {\tt bcx\_lo }, {\tt bcy\_lo }, {\tt bcz\_lo }, 
      {\tt bcx\_hi }, {\tt bcy\_hi }, {\tt bcz\_hi } are the boundary
   condition types at the lower (`{\tt lo}') and upper (`{\tt hi}')
   domain boundaries in the $x$, $y$, and $z$ coordinate directions.
   The different types are set via integer flags listed in table~\ref{arch:table:bcflags}.

   \begin{table}[h]
   \caption{\label{arch:table:bcflags} Boundary condition flags}  
   \begin{center}
   \begin{tabular}{ll}
   \hline
   BC type    & integer flag \\
   \hline
   periodic             & $-1$ \\
   inlet (user-defined) & $11$ \\
   outlet               & $12$ \\
   symmetry             & $13$ \\
   slip wall            & $14$ \\
   no-slip wall         & $15$ \\
   \hline
   \end{tabular}
   \end{center}
   \end{table}

@@

The first argument to the {\tt eos} call is an integer key that
specifies which thermodynamic variables (in addition to the mass
fractions) are used as input.  EOS input options are listed 
in table~\ref{arch:table:eosinput}.

   \begin{table}[h]
   \caption{\label{arch:table:eosinput} EOS input flags}
   \begin{center}
   \begin{tabular}{lc}
   \hline
   key            & input quantities \\
   \hline
   {\tt eos\_input\_rt}       & $\rho$, $T$ \\
   {\tt eos\_input\_rh}       & $\rho$, $h$ \\
   {\tt eos\_input\_tp}       & $T$, $p$ \\
   {\tt eos\_input\_rp}       & $\rho$, $p$ \\
   {\tt eos\_input\_re}       & $\rho$, $e$ \\
   {\tt eos\_input\_ps}       & $p$, $s$ \\
   \hline
   \end{tabular}
   \end{center}
   \end{table}

@@

The {\tt variables} module provides integer keys to index the state
multifabs and other arrays dealing with the scalar quantities.  The
most commonly used keys are are list in table~\ref{arch:table:variables}.

\begin{table}[h]
\caption{\label{arch:table:variables} Common {\tt variables} module keys}
\begin{center}
\begin{tabular}{ll}
\hline
{\tt rho\_comp}  & density \\
{\tt rhoh\_comp} & density $\times$ specific enthalpy, $(\rho h)$ \\
{\tt spec\_comp} & first species partial density, $(\rho X_1)$ \\
{\tt temp\_comp} & temperature \\
\hline
\end{tabular}
\end{center}
\end{table}
